%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Caleb Coffie's Resume/CV
% XeLaTeX Template
% Version 2.0 (1/22/15)
%
% Original author:
% Adrien Friggeri (adrien@friggeri.net)
% https://github.com/afriggeri/CV
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{CalebCoffie-CV-Class} % Add 'print' as an option into the square bracket to remove colors from this template for printing

\begin{document}

\header{Caleb}{Coffie}{Computer Security Buff \& Part-time Developer} % Your name and current job title/field

%----------------------------------------------------------------------------------------
%	SIDEBAR SECTION
%----------------------------------------------------------------------------------------

\begin{aside} % In the aside, each new line forces a line break
\section{Contact}
1855 Greenpoint Ave
Schenectady, NY 12303
~
+1 (518) 982 6860
~
\href{mailto:CalebCoffie@gmail.com}{CalebCoffie@gmail.com}
\href{https://CalebCoffie.com}{https://CalebCoffie.com}
\href{https://github.com/johnsmith}{github://CCoffie}
\section{Skills}
Python{\color{black} $\varheartsuit$}, Flask, Powershell, git, VMware Workstation \& VSphere, Clonezilla (DRBL)
\section{Relevant Courses}
\item Cryptography and Authentication
\item Cyber Defense Techniques
\item Humanitarian Free/Open Source Software
\item Free \& Open Source Culture
\item Information Security Policies
\item Risk Management for Information Security
\item Computer System Forensics
\item Windows System Forensics
\end{aside}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\section{Education}

\begin{entrylist}
%------------------------------------------------
\entry
{Expected Grad.\\May 2016}
{B.S. {\normalfont Computing Security}}
{Rochester Institute of Technology - Rochester, NY}
{Minor in Open Source \& Free Culture}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{entrylist}
%------------------------------------------------
\entry
{January 2014--\\August 2014}
{Wyman-Gordon Forging}
{Houston, Texas}
{\emph{IT/Networking Systems Administrator} \\
Supported over 500 users on Windows systems. Worked with users to troubleshoot issues with hardware, software and networking issues. Led the effort of transitioning 200+ Windows XP user and control systems to newer operating systems. Developed and maintained an imaging server that used to setup systems multiple plants around the country. Implemented various asset and device management systems.}
%------------------------------------------------
\entry
{September 2012--\\December 2013,\\August 2014--\\Now}
{RIT Center of Imaging Science}
{Rochester, NY}
{\emph{Student Systems Administrator} \\
Provided support for Student and Faculty using Mac OS X, Windows, and Linux systems. Imaged and deployed systems for new classes.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	PROJECTS SECTION
%----------------------------------------------------------------------------------------

\section{Projects}

\begin{entrylist}
%------------------------------------------------
\entry
{Winter 2015}
{Roastero}
{PennApps}
{Reverse engineered a USB controlled coffee roaster. Wrote a custom, cross-platform application in Python and PyQt which significantly extends the capabilities of the roaster, providing a thermostat-based controller and roast graphs.}
%------------------------------------------------
\entry
{Fall 2014}
{tldrcode.com}
{HackRPI}
{Created an open source Jekyll powered website, in a team of three at HackRPI. Site serves as a place for programmers to reference code syntax in a language they may not be familiar with. The site currently features 10 languages and has active community support.}
%------------------------------------------------
\entry
{Fall 2014}
{RemoteNotify}
{Windows System Forensics Class}
{Created an open source Windows service which notifies the user when someone has remoted into their system.}
%------------------------------------------------
\entry
{Spring 2014}
{Kippo-Graph}
{Open Source Project Contribution}
{Added a feature to the project called Kippo-PlayLog. This new featured allowed for an animated playback of the attacker’s SSH log within browser.}
%------------------------------------------------
\end{entrylist}

%----------------------------------------------------------------------------------------
%	ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\section{Activities}

\textbf{Clubs:} Security Practices and Research Asssociation (SPARSA) \textbf{Competitions:} Cyber Security Awareness Week (CSAW), Information Security Talent Search (ISTS), National Cyber League (NCL), Various Hackathons (HackRPI, PennApps, and More)

%----------------------------------------------------------------------------------------

%----------------------------------------------------------------------------------------
%	INTERESTS AND ACTIVITIES SECTION
%----------------------------------------------------------------------------------------

\section{Hobbies}

Church, Coffee, Hardware Hacking, Computer System Building, Quadcopters
%----------------------------------------------------------------------------------------

\end{document}